---
title: "Malaysia Enterprise Survey"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(plotly)
library(oidnChaRts)
library(highcharter)
library(readstata13)
library(ggplot2)
setwd("C:/Users/Lelo/Google Drive/Big Data/WB Enterprise Surveys")
ES2015MY <- read.dta13("Malaysia-2015-full data LN.dta")
```

## Introduction

This post is the first in a series of my analysis of the 2015 Enterprise Surveys conducted by the World Bank. I obtained the data set directly from Enterprise Surveys (http://www.enterprisesurveys.org), The World Bank, for research purposes.

The Enterprise Surveys use standard survey instruments to collect firm-level data on the business environment from business owners and top managers. The surveys cover a broad range of topics including access to finance, corruption, infrastructure, crime, competition, labor, obstacles to growth, and performance measures. Below is a distribution of firms surveyed by region and business type. You can hover your mouse over each bar to get more information:

```{r}
ES2015MY %>%
  group_by(region, b1) %>%
  summarise(total = sum(id)) %>%
  ungroup() %>%
  hchart("bar",
         hcaes(y = total,
               x = region,
               group = b1)) %>%
  hc_plotOptions(series = list(stacking = "stack"))
```

The above illustrates that the bulk of the firms surveyed are from the Central region, which includes the Klang Valley and the capital Kuala Lumpur. The North, inclusive of Penang follows in second place. Partnerships are the most common business type among the firms surveyed. Sole Proprietorships are also common. Below is a breakdown of shares of business types surveyed by region:
```{r}
ES2015MY %>%
  group_by(region, b1) %>%
  summarise(total = sum(id)) %>%
  ungroup() %>%
  hchart("bar",
         hcaes(y = total,
               x = region,
               group = b1)) %>%
  hc_plotOptions(series = list(stacking = "percent")) %>%
  hc_tooltip(shared = TRUE)
```

Data Source: Enterprise Surveys (http://www.enterprisesurveys.org), The World Bank
