---
title: "Obstacles to Enterprise Success"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(plotly)
library(oidnChaRts)
library(highcharter)
library(readstata13)
library(ggplot2)
setwd("C:/Users/Lelo/Google Drive/Big Data/WB Enterprise Surveys")
ES2015MY <- read.dta13("Malaysia-2015-full data LN.dta")
```

## Introduction

This post is the third in a series of my analysis of the 2015 Enterprise Surveys conducted by the World Bank. I obtained the data set directly from Enterprise Surveys (http://www.enterprisesurveys.org), The World Bank, for research purposes.

## Biggest Obstacle to Enterprise Operations
When asked what the main obstacles to business was here is what firms across the 5 regions had to say:
```{r}
library(car)
library(RColorBrewer)
 
# Let's use the car dataset proposed by R
data=mtcars
 
# Make the plot
my_colors <- brewer.pal(nlevels(as.factor(data$cyl)), "Set2")
scatterplotMatrix(~mpg+disp+drat|cyl, data=data , reg.line="" , smoother="", col=my_colors , smoother.args=list(col="grey") , cex=1.5 , pch=c(15,16,17) , main="Scatter plot with Three Cylinder Options")
```

Most state that competition from firms in the informal sector is the main challenge. In the East Coast of Peninsular Malaysia, it was Business Licensing and Permits. In Sabah/Sarawak, firms stated Customs and Trade Regulations, in addition to Practices of Informal Firms and Tax Rates.

Data Source: Enterprise Surveys (http://www.enterprisesurveys.org), The World Bank
