---
title: "Obstacles to Enterprise Success"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(plotly)
library(oidnChaRts)
library(highcharter)
library(readstata13)
library(ggplot2)
setwd("C:/Users/Lelo/Google Drive/Big Data/WB Enterprise Surveys")
ES2015MY <- read.dta13("Malaysia-2015-full data LN.dta")
```

## Introduction

This post is the third in a series of my analysis of the 2015 Enterprise Surveys conducted by the World Bank. I obtained the data set directly from Enterprise Surveys (http://www.enterprisesurveys.org), The World Bank, for research purposes.

## Biggest Obstacle to Enterprise Operations
When asked what the main obstacles to business was here is what firms across the 5 regions had to say:
```{r}
ES2015MY %>%
  group_by(region, obstacle) %>%
  summarise(total = sum(id)) %>%
  ungroup() %>%
  hchart("bar",
         hcaes(y = total,
               x = region,
               group = obstacle)) %>%
  hc_plotOptions(series = list(stacking = "percent")) %>%
  hc_tooltip(shared = TRUE)
```

Most state that competition from firms in the informal sector is the main challenge. In the East Coast of Peninsular Malaysia, it was Business Licensing and Permits. In Sabah/Sarawak, firms stated Customs and Trade Regulations, in addition to Practices of Informal Firms and Tax Rates.

Data Source: Enterprise Surveys (http://www.enterprisesurveys.org), The World Bank
